%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{David}{Campbell}{ % Your name
\urlstyle{same}\url{https://www.linkedin.com/pub/david-campbell/78/135/712} \\ % Your website, LinkedIn profile or other web address
\href{davidcampbell633@gmail.com}{davidcampbell633@gmail.com} | 774.454.8904 % Your contact information
}



%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page


\section{Summary}
Looking for a summer internship to prepare for physics graduate school.

\sectionspace

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{UMass Lowell}

\descript{Bachelor of Science, Double Major Physics and Mathematics}
\location{Expected August 2015 | Cum. GPA: 3.80}


\sectionspace % Some whitespace after the section

%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}

\subsection{Physics}
 Waves and Optics, Electromagnetism I and II, Intro to Quantum Mechanics I and II, Statistical Thermodynamics, Modern Physics, Classical Mechanics

\subsection{Mathematics}
Mathematics of Signal Processing, Linear Algebra I and II, Probability and Statistics I, Applied Math I and II, Complex Variables, Partial Differential Equations, Discrete Structures\\

\sectionspace % Some whitespace after the section

\section{Computer Skills}



Matlab \textbullet{} Python \textbullet{} LabVIEW  \textbullet{} C \textbullet{} \LaTeX\ \textbullet{} XML \textbullet AutoCAD \textbullet Shell\\
\location{Familiar:}
Mathematica \textbullet{} MathCAD \textbullet{} Unix \textbullet{} Windows

\sectionspace % Some whitespace after the section

\section{Awards}
Arthur Zamanakos Scholarship (excellence in Mathematics) \textbullet{} Ye-Yung Teng Memorial Scholarship (excellence in Physics) \textbullet{} Kennedy Family Merit Scholarship (June 2012, June 2013)

\section{Interests}
Acting, golfing, basketball,\\
and chess.

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page



%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{Draper Laboratories}
\descript{| Sensors and Imaging Systems Co-Op}
\location{Jan. 2014 – May 2014 | Cambridge, MA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
 \item Wrote a Monte Carlo simulation in Matlab to model shot and background noise in an image sensor, and the uncertainty in the image center.
      \item Used a schematic to order, build, and set up a wireless sensor network.
      \item Set up hardware to test CMOS sensors, and developed an interface in Python that linked the frame grabber of the sensor to the motion of the interacting laser.
      \item Improved an electro-optical computer model by integrating a Python package for unit parsing and writing XML files for easy data importation.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------


%------------------------------------------------
% Research
%------------------------------------------------

\section{Research}

\runsubsection{AMO Physics Lab}
\descript{| REU University of Oklahoma }
\location{ June 2014 – July 2014 | Norman, OK}
\begin{tightitemize}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\item Worked with \textbf{\href{https://www.nhn.ou.edu/~shaffer/research/}{Prof. James Shaffer's}} quantum optics to develop micro-machining methods for fabricating atom chips. 
\item Varied milling parameters of a micro-machine, and analyzed test cuts to determine which parameters produced the finest features. 
\item Presented findings to the OU physics faculty.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

%\runsubsection{Explorations in Quasi-Randomness}
%\descript{| Undergraduate Researcher and Co-Founder}
%\location{Oct. 2012 – Dec. 2013 | Lowell, MA} 
%\begin{tightitemize}
%\vspace{\topsep}
%\item Initiated the start up of the group with \textbf{\href{http://faculty.uml.edu/jpropp/}{Prof. James Propp}} and recruited students to join. 
%\item Worked in a small group on combinatorics problems related to the de-randomized Polya and Smirnov boards. 
%\item Presented work at an undergraduate mathematics conference.
%\end{tightitemize}

\sectionspace % Some whitespace after the section

\section{Lab Work}

\runsubsection{Physics of Materials and Devices}
%\descript{| Fall 2012}
\location{    }
\begin{tightitemize}
\item Designed circuitry to characterize electrical devices and materials such as op-
erational amplifiers, active filters, diodes and semiconductors.
\item Applied an input signal to the circuit and varied its frequency and amplitude.
\item Observed, collected, and analyzed data from the varying  output signal, due to input modifications, to determine the properties of the device or material.
\end{tightitemize}

\sectionspace

\runsubsection{Principles of lab Automation}
%\descript{| Spring 2013}
\location{   }
\begin{tightitemize}
   \item Implemented LabVIEW software by setting up the experimental hardware to
conduct a computer-controlled experiment that would acquire and display data.
\item Analyzed the acquired data to determine the AC response of mutual inductors, RC circuits, and LRC circuits.
%\item Analyzed the collected data to determine  properties of the electronic device or circuit. 
\end{tightitemize}

\sectionspace

\runsubsection{Advanced Physics Lab I}
%\descript{| Fall 2013}
\location{    }
\begin{tightitemize}
\item Used advanced experimental hardware, such as the Michelson Interferometer and Prism Spectrometer, to make precise measurements of physical constants. 
\item Maintained an up-to-date laboratory notebook of qualitative and quantitative observations made during the experiments.
\item Wrote formal papers that summarized the experimental measurements, with data tables and graphs, and used statistics to analyze the results.
%\item Implemented LabVIEW software by setting up the experimental hardware to conduct a computer-controlled experiment that would acquire and display data.
\end{tightitemize}


%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}